\documentclass{ujarticle}
\usepackage{docmute}
\usepackage{sotsuron}

\begin{document}
\input{0_title_kitamori}
\input{1_intro}
\input{2_ANFIS_Classifier}
\input{3_Robust_ANFIS}
\input{4_Numerical_Experiment}
\input{5_Conclusions}


\begin{thebibliography}{99}
\bibitem{Jang1993}
Jang, J.-S. R.: ANFIS: Adaptive-network-based fuzzy inference system. IEEE Transactions on Systems, Man and Cybernetics, \textbf{23}(3), 665--685 (1993)

\bibitem{Takagi1985}
Takagi, T., Sugeno, M.: Fuzzy identification of systems and its applications to modeling and control. IEEE Transactions on Systems, Man and Cybernetics, \textbf{15}, 116--132 (1985)

\bibitem{Angelov2004}
Angelov, P., Xydeas, C., Filev, D.: On-line identification of MIMO evolving Takagi-Sugeno fuzzy models. In: 2004 IEEE International Conference on Fuzzy Systems, \textbf{1}, 55--60, (2004)

\bibitem{Honda_ICIEV2021}
Honda, K., Hyakutake, S., Ubukata, S., Notsu, A.: A hybrid robust ANFIS based on noise fuzzy clustering, In: 10th International Conference on Informatics, Electronics \& Vision and 5th International Conference on Imaging, Vision \& Pattern Recognition, \textbf{81}, 1--7 (2021)

\bibitem{Bezdek81a}
Bezdek, J. C.: Pattern Recognition with Fuzzy Objective Function Algorithms, Plenum Press (1981)

\bibitem{Miyamoto_book08}
Miyamoto, S., Ichihashi, H., Honda, K.: Algorithms for Fuzzy Clustering, Springer (2008)

\bibitem{Dave91}
Dav\'e, R. N.: Characterization and detection of noise in clustering. Pattern Recognition Letters, \textbf{12}(11), 657--664 (1991)

\bibitem{Dave97}
Dav\'e, R. N., Krishnapuram, R.: Robust clustering methods: a unified view. IEEE Trans. on Fuzzy Systems, \textbf{5}, 270--293 (1997)

\bibitem{Holland77}
Holland, P. W., Welsch, R. E.: Robust regression using iteratively reweighted least-squares. Communications in Statistics, \textbf{A6}(9), 813--827 (1977)

\bibitem{Honda2010_IEEE-TFS}
Honda, K., Notsu, A., Ichihashi, H.: Fuzzy PCA-guided robust $k$-means clustering. IEEE Trans. Fuzzy Systems, \textbf{18}(1), 67--79 (2010)

\bibitem{Angelov2008}
Angelov, P. P., Zhou, X.: Evolving fuzzy-rule-based classifiers from data streams. IEEE Transactions on Fuzzy Systems, \textbf{16}(6), 1462--1475 (2008)

\bibitem{MacQueen67}
MacQueen, J. B.: Some methods of classification and analysis of multivariate observations. Proc. of 5th Berkeley Symposium on Math. Stat. and Prob., 281--297 (1967)

\bibitem{Krishnapuram93}
Krishnapuram, R., Keller, J. M.: A possibilistic approach to clustering. IEEE Trans. on Fuzzy Systems,  \textbf{1}, 98--110 (1993)

\bibitem{UCI_repository2019}
Dua, D., Graff, C.: UCI Machine Learning Repository. Irvine, CA: University of California, School of Information and Computer Science (2019)  \url{http://archive.ics.uci.edu/ml} Last accessed 30 Nov 2021

\end{thebibliography}
\end{document}
